---
title: "TRESH_RQ1_Analysis"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    theme: spacelab
fontsize: 16pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages
```{r Load Packages, message=TRUE, warning=TRUE}
# load packages
install.packages("pacman", repos = "http://cran.us.r-project.org")
library(pacman)
p_load(tidyverse, ggridges, ggplot2, patchwork, rstatix, reshape2, ggdist, easystats, ordinal, lme4, apaTables, car, robustlmm)

options(scipen=30000)
```

## Load Data
```{r Load Data, echo=TRUE}
# load in datafiles

df_survey <- read.csv("dataframes/softbots_study1.csv", header=TRUE)
# remove added x column
df_survey <- df_survey[-1]

df_unique <- read.csv("dataframes/df_unique.csv", header=TRUE)
# remove added x column
df_unique <- df_unique[-1]
```

## Variable transformation
```{r}
# Bring variables into right format

# factors
df_survey <- df_survey %>%
  mutate(across(c(ParticipantID, consent, gender, country, teach.school, robot, robot_type, starts_with("rank"),starts_with("suit"),starts_with("favorite"), attentioncheck1, attentioncheck2, source, videos.amount, movies.amount, robots.skepticism), as.factor))

# numeric
df_survey <- df_survey %>%
  mutate(across(c(starts_with("prior"), teach.age_1, teach.age_2,teach.age_3,teach.age_4,teach.age_5,teach.age_6,teach.subject_1,teach.subject_2,teach.subject_3,teach.subject_4,teach.subject_5,teach.subject_6,teach.subject_7,teach.subject_8,teach.subject_9,teach.subject_10, Views, Viewssuit, totalviews),as.numeric
  ))
```

# Correlations
```{r}
df_cor <- df_survey[,c(7,81:96,110:113)]

# rename variables
df_cor <- df_cor %>%
  dplyr::rename(
    "Age" = age,
    "Familiarity to robot" = familiarrobot,
    "Familiarity to objects" = familiarobjec,
    "Safety" = safety,
    "Competence" = competence,
    "Comfortable around" = comfortable,
    "Friendliness" = friendliness,
    "Creepy/Cute" = creepycute,
    "Bad/Good" = badgood,
    "Physical warmth" = physicalwarm,
    "Social warmth" = socialwarm,
    "Human-like form" = humanform,
    "Human-like motion" = humanmotion,
    "Social competence" = socialcompetence,
    "Socialness" = socialness,
    "Social intelligence" = socialintelligence,
    "Intelligence" = intelligence,
    "Suitability math" = suitmath,
    "Suitability diff. task" = suitdifftask,
    "Suitability reading" = suitread,
    "Suitability art" = suitart
  )

#create table
apa.cor.table(df_cor, filename="Tables/Dimensions_correlations.doc", table.number=1)
```

# Means
```{r}
# hard coded as 1, soft as 2

# reshape to long
df_long_dimensions <- tidyr::pivot_longer(df_survey, cols = c("familiarrobot","familiarobjec","safety","competence","comfortable","friendliness","creepycute","badgood","physicalwarm","socialwarm","humanform","humanmotion","socialcompetence","socialness","socialintelligence","intelligence"), names_to = "dimension", values_to = "value")
```

## Means per dimension
```{r}
# calculate means per dimension 
df_unique%>%
  get_summary_stats(c(badgood,comfortable,competence,creepycute,familiarobjec,familiarrobot,friendliness,humanform,humanmotion,intelligence,physicalwarm,safety,socialcompetence,socialintelligence,socialness,socialwarm), type = "mean_sd")
```

## Means per robot type
```{r}
# means per dimension and robot type
means_robottype <- df_survey%>%
  group_by(robot_type) %>%
  get_summary_stats(c(badgood,comfortable,competence,creepycute,familiarobjec,familiarrobot,friendliness,humanform,humanmotion,intelligence,physicalwarm,safety,socialcompetence,socialintelligence,socialness,socialwarm), type = "mean_sd")

means_robottype
```

## Means per robot
```{r}
# means per dimension per robot
means_robot <- df_long_dimensions %>%
  group_by(robot, dimension) %>%
  get_summary_stats(value, type = "mean_sd")

means_robot
```

# LMERs
```{r}
# set sum-to-zero contrasts
contrasts(df_survey$robot_type) <- contr.sum 
contrasts(df_survey$robot_type)
```

## Bad/good
```{r LMER_badgood}
# run lmer
model_badgood <- lmer(badgood ~ robot_type + (1 + robot_type | ParticipantID) + (1|robot), data = df_survey)

# print results
summary(model_badgood)

# calculate cCIs
confint(model_badgood, level = 0.95, method = 'profile')

# model diagnostics
check_model(model_badgood)
res_model_badgood <- residuals(model_badgood)
qqPlot(res_model_badgood)
```
## Comfortable 
```{r LMER_comfortable}
model_comfortable<- lmer(comfortable ~ robot_type + (1 + robot_type | ParticipantID) + (1|robot), data = df_survey)

summary(model_comfortable)
confint(model_comfortable, level = 0.95, method = 'profile')

# model diagnostics
check_model(model_comfortable)
res_model_comfortable <- residuals(model_comfortable)
qqPlot(res_model_comfortable)
```

## Competence
```{r LMER_competence}
model_competence<- lmer(competence ~ robot_type + (1 + robot_type | ParticipantID) + (1|robot), data = df_survey)

summary(model_competence)
confint(model_competence, level = 0.95, method = 'profile')

# model diagnostics
check_model(model_competence)

res_model_competence <- residuals(model_competence)
qqPlot(res_model_competence)
```

## Creepy/Cute
```{r LMER_creepycute, warning=FALSE}
model_creepycute<- lmer(creepycute ~ robot_type + (1 + robot_type | ParticipantID) + (1|robot), data = df_survey)

summary(model_creepycute)
confint(model_creepycute, level = 0.95, method = 'profile')

# model diagnostics
check_model(model_creepycute)

res_model_creepycute <- residuals(model_creepycute)
qqPlot(res_model_creepycute)
```

## Familiarity objects
```{r LMER_familiarityobject}
model_familiarobj<- lmer(familiarobjec ~ robot_type + (1 + robot_type | ParticipantID) + (1|robot), data = df_survey)

summary(model_familiarobj)
confint(model_familiarobj, level = 0.95, method = 'profile')

# model diagnostics
check_model(model_familiarobj)

res_model_familiarobj <- residuals(model_familiarobj)
qqPlot(res_model_familiarobj)
```

## Familiarity robots
```{r LMER_familiarityrobots}
model_familiarrobo<- lmer(familiarrobot ~ robot_type + (1 + robot_type | ParticipantID) + (1|robot), data = df_survey)

summary(model_familiarrobo)
confint(model_familiarrobo, level = 0.95, method = 'profile')

# model diagnostics
check_model(model_familiarrobo)

res_model_familiarrobo <- residuals(model_familiarrobo)
qqPlot(res_model_familiarrobo) # slight deviation

# robust lmer
model_familiarrobo_robust <- rlmer(familiarrobot ~ robot_type + (1 + robot_type | ParticipantID) + (1|robot), data = df_survey)

summary(model_familiarrobo_robust)

# calculate Wald confidence interval, since assumptins are violated, https://gist.github.com/kamermanpr/aaa598485b6e990017375359ff5f4533
confint.rlmerMod <- function(object, level = 0.95) {
  
  # Extract beta coefficients
  beta <- fixef(object)
  
  # Extract names of coefficients
  parm <- names(beta)
  
  # Extract standard errors for the coefficients
  se <- sqrt(diag(vcov(object)))
  
  # Set level of confidence interval
  z <- qnorm((1 + level) / 2)
  
  # Calculate CI
  ctab <- cbind(beta - (z * se), 
                beta + (z * se))
  
  # label column names
  colnames(ctab) <- c(paste(100 * ((1 - level) / 2), '%'),
                      paste(100 * ((1 + level) / 2), '%'))
  
  # Output
  return(ctab[parm, ])
}

confint.rlmerMod(model_familiarrobo_robust) 

check_model(model_familiarrobo_robust)
```

## Friendliness
```{r LMER_friendliness}
model_friendliness<- lmer(friendliness ~ robot_type + (1 + robot_type | ParticipantID) + (1|robot), data = df_survey)

summary(model_friendliness)
confint(model_friendliness, level = 0.95, method = 'profile')

# model diagnostics
check_model(model_friendliness)

res_model_friendliness <- residuals(model_friendliness)
qqPlot(res_model_friendliness)
```

## Human-like form
```{r LMER_humanform}
model_humanform<- lmer(humanform ~ robot_type + (1 + robot_type | ParticipantID) + (1|robot), data = df_survey)

summary(model_humanform)
confint(model_humanform, level = 0.95, method = 'profile')

# model diagnostics
check_model(model_humanform)

res_model_humanform <- residuals(model_humanform)
qqPlot(res_model_humanform)
```
## Human-like motion
```{r LMER_humanmotion}
model_humanmotion<- lmer(humanmotion ~ robot_type + (1 + robot_type | ParticipantID) + (1|robot), data = df_survey)

summary(model_humanmotion)
confint(model_humanmotion, level = 0.95, method = 'profile')

# model diagnostics
check_model(model_humanmotion)

res_model_humanmotion <- residuals(model_humanmotion)
qqPlot(res_model_humanmotion)
```

## Intelligence
```{r LMER_intelligence}
model_intelligence<- lmer(intelligence ~ robot_type + (1 + robot_type | ParticipantID) + (1|robot), data = df_survey)

summary(model_intelligence)
confint(model_intelligence, level = 0.95, method = 'profile')

# model diagnostics
check_model(model_intelligence)

res_model_intelligence <- residuals(model_intelligence)
qqPlot(res_model_intelligence)
```
## Physical warmth
```{r LMER_physicalwarmth}
model_physicalwarm<- lmer(physicalwarm ~ robot_type + (1 + robot_type | ParticipantID) + (1|robot), data = df_survey)

summary(model_physicalwarm)
confint(model_physicalwarm, level = 0.95, method = 'profile')

# model diagnostics
check_model(model_physicalwarm)

res_model_physicalwarm <- residuals(model_physicalwarm)
qqPlot(res_model_physicalwarm)
```

## Safety
```{r LMER_safety}
model_safety<- lmer(safety ~ robot_type + (1 + robot_type | ParticipantID) + (1|robot), data = df_survey)

summary(model_safety)
confint(model_safety, level = 0.95, method = 'profile')

# model diagnostics
check_model(model_safety)

res_model_safety <- residuals(model_safety)
qqPlot(res_model_safety)
```

## Social competence
```{r LMER_socialcompetence}
model_socialcompetence<- lmer(socialcompetence ~ robot_type + (1 + robot_type | ParticipantID) + (1|robot), data = df_survey)

summary(model_socialcompetence)
confint(model_socialcompetence, level = 0.95, method = 'profile')

# model diagnostics
check_model(model_socialcompetence)

res_model_socialcompetence <- residuals(model_socialcompetence)
qqPlot(res_model_socialcompetence)
```

## Social intelligence
```{r LMER_socialintelligence}
model_socialintelligence<- lmer(socialintelligence ~ robot_type + (1 + robot_type | ParticipantID) + (1|robot), data = df_survey)

summary(model_socialintelligence)
confint(model_socialintelligence, level = 0.95, method = 'profile')

# model diagnostics
check_model(model_socialintelligence)

res_model_socialintelligence <- residuals(model_socialintelligence)
qqPlot(res_model_socialintelligence)
```

## Socialness
```{r LMER_socialness}
model_socialness<- lmer(socialness ~ robot_type + (1 + robot_type | ParticipantID) + (1|robot), data = df_survey)

summary(model_socialness)
confint(model_socialness, level = 0.95, method = 'profile')

# model diagnostics
check_model(model_socialness)

res_model_social <- residuals(model_socialness)
qqPlot(res_model_social)
```

## Social warmth
```{r LMER_socialwarmth}
model_socialwarm<- lmer(socialwarm ~ robot_type + (1 + robot_type | ParticipantID) + (1|robot), data = df_survey)

summary(model_socialwarm)
confint(model_socialwarm, level = 0.95, method = 'profile')

# model diagnostics
check_model(model_socialwarm)

res_model_socialwarm <- residuals(model_socialwarm)
qqPlot(res_model_socialwarm)
```

# CLMMs
## Bad/good
```{r}
model_clmm_badgood <- clmm(rankbadgood ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey) 

summary(model_clmm_badgood)

# profile CI
confint(model_clmm_badgood, level=0.95, type=profile)
```

## Comfortable
```{r}
model_clmm_comfortable <- clmm(rankcomfortable ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey) 

summary(model_clmm_comfortable)

# profile CI
confint(model_clmm_comfortable, level=0.95, type=profile)
```

## Competence
```{r}
model_clmm_competence <- clmm(rankcompetence ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey) 

summary(model_clmm_competence)

# profile CI
confint(model_clmm_competence, level=0.95, type=profile)
```

## Creepy/Cute
```{r}
model_clmm_creepycute <- clmm(rankcreepycute ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey) 

summary(model_clmm_creepycute)

# profile CI
confint(model_clmm_creepycute, level=0.95, type=profile)
```

## Friendliness
```{r}
model_clmm_friendliness <- clmm(rankfriendliness ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey) 

summary(model_clmm_friendliness)

# profile CI
confint(model_clmm_friendliness, level=0.95, type=profile)
```

## Human-like form
```{r}
model_clmm_humanform <- clmm(rankhumanform ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey) 

summary(model_clmm_humanform) 

# profile CI
confint(model_clmm_humanform, level=0.95, type=profile)
```

## Intelligence
```{r}
model_clmm_intelligence <- clmm(rankintelligence ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey) 

summary(model_clmm_intelligence)

# profile CI
confint(model_clmm_intelligence, level=0.95, type=profile)
```

## Physical warmth
```{r}
model_clmm_physicalwarm <- clmm(rankphysicalwarmth ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey) 

summary(model_clmm_physicalwarm)

# profile CI
confint(model_clmm_physicalwarm, level=0.95, type=profile)
```

## Safety
```{r}
model_clmm_safety <- clmm(ranksafety ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey) 

summary(model_clmm_safety)

# profile CI
confint(model_clmm_safety, level=0.95, type=profile)
```

## Social competence
```{r}
model_clmm_socialcomp <- clmm(ranksocialcompetence ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey) 

summary(model_clmm_socialcomp)

# profile CI
confint(model_clmm_socialcomp, level=0.95, type=profile)
```

## Social intelligence
```{r}
model_clmm_socialint <- clmm(ranksocialintelligence ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey) 

summary(model_clmm_socialint)

# profile CI
confint(model_clmm_socialint, level=0.95, type=profile)
```

## Socialness
```{r}
model_clmm_socialness <- clmm(ranksocial ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey) 

summary(model_clmm_socialness)

# profile CI
confint(model_clmm_socialness, level=0.95, type=profile)
```

## Social warmth
```{r}
model_clmm_socialwarm <- clmm(ranksocialwarmth ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey) 

summary(model_clmm_socialwarm)

# profile CI
confint(model_clmm_socialwarm, level=0.95, type=profile)
```

# GLMERs
```{r}
# create new rank variable with 1 for being ranked 1st and 0 for not being ranked first

df_survey <- df_survey %>%
  mutate(rank_glmer_goodbad = dplyr::case_when(
                                        rankbadgood == "1" ~ "1", 
                                        rankbadgood != "1" ~ "0", 
                                       ),
         rank_glmer_comfortable = dplyr::case_when(
                                        rankcomfortable == "1" ~ "1", 
                                        rankcomfortable != "1" ~ "0", 
                                       ),
         rank_glmer_competence = dplyr::case_when(
                                        rankcompetence == "1" ~ "1", 
                                        rankcompetence != "1" ~ "0",),
         rank_glmer_creepycute = dplyr::case_when(
                                        rankcreepycute == "1" ~ "1", 
                                        rankcreepycute != "1" ~ "0", 
                                       ),
         rank_glmer_friendliness = dplyr::case_when(
                                        rankfriendliness == "1" ~ "1", 
                                        rankfriendliness != "1" ~ "0", 
                                       ),
         rank_glmer_humanform = dplyr::case_when(
                                        rankhumanform == "1" ~ "1", 
                                        rankhumanform != "1" ~ "0", 
                                       ),
         rank_glmer_intelligence = dplyr::case_when(
                                        rankintelligence == "1" ~ "1", 
                                        rankintelligence != "1" ~ "0", 
                                       ),
         rank_glmer_physicalwarm = dplyr::case_when(
                                        rankphysicalwarmth == "1" ~ "1", 
                                        rankphysicalwarmth != "1" ~ "0", 
                                       ),
         rank_glmer_safety = dplyr::case_when(
                                        ranksafety == "1" ~ "1", 
                                        ranksafety != "1" ~ "0", 
                                       ),
         rank_glmer_socialcompetence = dplyr::case_when(
                                        ranksocialcompetence == "1" ~ "1", 
                                        ranksocialcompetence != "1" ~ "0", 
                                       ),
         rank_glmer_socialintelligence = dplyr::case_when(
                                        ranksocialintelligence == "1" ~ "1", 
                                        ranksocialintelligence != "1" ~ "0", 
                                       ),
         rank_glmer_social= dplyr::case_when(
                                        ranksocial == "1" ~ "1", 
                                        ranksocial != "1" ~ "0", 
                                       ),
         rank_glmer_socialwarmth = dplyr::case_when(
                                        ranksocialwarmth == "1" ~ "1", 
                                        ranksocialwarmth != "1" ~ "0", 
                                       )
         )

# turn into numeric
df_survey <- df_survey %>%
  mutate(across(c(starts_with("rank_glmer")),as.numeric
  ))
```

## Bad/Good
```{r}
model_glmer_badgood1 <- glmer(rank_glmer_goodbad ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey, family=binomial("logit"))

# singularity warning, so use maximal complex random intercepts instead
model_glmer_badgood2 <- glmer(rank_glmer_goodbad ~ robot_type + (1 | ParticipantID) + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit"))

# still warning, reduce
model_glmer_badgood3 <- glmer(rank_glmer_goodbad ~ robot_type + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit"))

# still warning, use allFit command
model_allfit1 <- allFit(model_glmer_badgood1) # all issue warnings
### save summary in new object
summ_allfit1 <- summary(model_allfit1) 
### look at fixed estimates
summ_allfit1$fixef # differences relatively small
### look at random effect
summ_allfit1$sdcor # differences small
### check log likelihood
summ_allfit1$llik
### check whether all model ran
summ_allfit1$which.OK # all ran

# use bobyqa
model_glmer_badgood_bobyqa <- glmer(rank_glmer_goodbad ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey, family=binomial("logit"), control = glmerControl(optimizer="bobyqa")) # no singularity warning anymore

summary(model_glmer_badgood_bobyqa) # not significant

# wald CI
confint(model_glmer_badgood_bobyqa,parm="beta_",method="Wald")
```

## Competence
```{r}
model_glmer_competence1 <- glmer(rank_glmer_competence ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey, family=binomial("logit"))

# singularity warning, so use maximal complex random intercepts instead
model_glmer_competence2 <- glmer(rank_glmer_competence ~ robot_type + (1 | ParticipantID) + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit"))

# still warning, reduce
model_glmer_competence3 <- glmer(rank_glmer_competence ~ robot_type + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit"))

# allfit command
model_allfit_comp1 <- allFit(model_glmer_competence1)
### save summary in new object
summ_allfit_comp1 <- summary(model_allfit_comp1) 
### look at fixed estimates
summ_allfit_comp1$fixef # differences relatively small
### look at random effect
summ_allfit_comp1$sdcor # differences small
### check log likelihood
summ_allfit_comp1$llik # differences small
### check whether all model ran
summ_allfit_comp1$which.OK # all ran 
# -> continue with singularity warning

summary(model_glmer_competence1) # significant

# wald CI
confint(model_glmer_competence1,parm="beta_",method="Wald")
```

## Comfortable
```{r}
model_glmer_comfortable1 <- glmer(rank_glmer_comfortable ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey, family=binomial("logit"))

# singularity warning, so use maximal complex random intercepts instead
model_glmer_comfortable2 <- glmer(rank_glmer_comfortable ~ robot_type + (1 | ParticipantID) + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit"))

# still warning, reduce
model_glmer_comfortable3 <- glmer(rank_glmer_comfortable ~ robot_type + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit"))

# allfit command
model_allfit_comf1 <- allFit(model_glmer_comfortable1)
### save summary in new object
summ_allfit_comf1 <- summary(model_allfit_comf1) 
### look at fixed estimates
summ_allfit_comf1$fixef # differences relatively small
### look at random effect
summ_allfit_comf1$sdcor # differences small
### check log likelihood
summ_allfit_comf1$llik # differences small
### check whether all model ran
summ_allfit_comf1$which.OK # all ran 
# -> continue with singularity warning

summary(model_glmer_comfortable1) # not significant

# wald CI
confint(model_glmer_comfortable1,parm="beta_",method="Wald")
```

## Friendliness
```{r}
# rank_glmer_friendliness
model_glmer_friendliness <- glmer(rank_glmer_friendliness ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey, family=binomial("logit"))

summary(model_glmer_friendliness)

# wald CI
confint(model_glmer_friendliness,parm="beta_",method="Wald")
```

## Human-like form
```{r}
# rank_glmer_humanform
model_glmer_humanform1 <- glmer(rank_glmer_humanform ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey, family=binomial("logit"))

# convergence warning, so use maximal complex random intercepts instead
model_glmer_humanform2 <- glmer(rank_glmer_humanform ~ robot_type + (1 | ParticipantID) + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit")) # singularity warning

# still warning, reduce
model_glmer_humanform3 <- glmer(rank_glmer_humanform ~ robot_type + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit"))

# allfit command
model_allfit_humanform1 <- allFit(model_glmer_humanform1)
### save summary in new object
summ_allfit_humanform1 <- summary(model_allfit_humanform1) 
### look at fixed estimates
summ_allfit_humanform1$fixef # differences large
### look at random effect
summ_allfit_humanform1$sdcor # differences large
### check log likelihood
summ_allfit_humanform1$llik # differences large
### check whether all model ran
summ_allfit_humanform1$which.OK # all ran 
# -> Redo with reduced model

# allfit command
model_allfit_humanform2 <- allFit(model_glmer_humanform2)
### save summary in new object
summ_allfit_humanform2 <- summary(model_allfit_humanform2) 
### look at fixed estimates
summ_allfit_humanform2$fixef # small differences 
### look at random effect
summ_allfit_humanform2$sdcor # small differences
### check log likelihood
summ_allfit_humanform2$llik # small differences
### check whether all model ran
summ_allfit_humanform2$which.OK # 
# -> continue with singularity warning of reduced model

summary(model_glmer_humanform2) # significant

# wald CI
confint(model_glmer_humanform2,parm="beta_",method="Wald")
```

## Creepy/cute
```{r}
model_glmer_creepycute1 <- glmer(rank_glmer_creepycute ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey, family=binomial("logit"))

# singularity warning, so use maximal complex random intercepts instead
model_glmer_creepycute2 <- glmer(rank_glmer_creepycute ~ robot_type + (1 | ParticipantID) + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit"))

# still warning, reduce
model_glmer_creepycute3 <- glmer(rank_glmer_creepycute ~ robot_type + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit"))

# allfit command
model_allfit_creepy1 <- allFit(model_glmer_creepycute1)
### save summary in new object
summ_allfit_creepy1 <- summary(model_allfit_creepy1) 
### look at fixed estimates
summ_allfit_creepy1$fixef # differences relatively small
### look at random effect
summ_allfit_creepy1$sdcor # differences small
### check log likelihood
summ_allfit_creepy1$llik # differences small
### check whether all model ran
summ_allfit_creepy1$which.OK # all ran 
# -> continue with singularity warning

summary(model_glmer_creepycute1) # significant

# wald CI
confint(model_glmer_creepycute1,parm="beta_",method="Wald")
```

## Intelligence
```{r}
model_glmer_intelligence1 <- glmer(rank_glmer_intelligence ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey, family=binomial("logit"))

# singularity warning, so use maximal complex random intercepts instead
model_glmer_intelligence2 <- glmer(rank_glmer_intelligence ~ robot_type + (1 | ParticipantID) + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit"))

# still warning, reduce
model_glmer_intelligence3 <- glmer(rank_glmer_intelligence ~ robot_type + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit"))

# allfit command
model_allfit_int1 <- allFit(model_glmer_intelligence1)
# -> nmkbw doesnt issue warning

# use nmkbw
model_glmer_intelligence_nmkbw <- glmer(rank_glmer_intelligence ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey, family=binomial("logit"), control = glmerControl(optimizer="nmkbw")) # no singularity warning 

summary(model_glmer_intelligence_nmkbw) # not significant

# wald CI
confint(model_glmer_intelligence_nmkbw,parm="beta_",method="Wald")
```

## Physical warmth
```{r}
model_glmer_physicalwarm1 <- glmer(rank_glmer_physicalwarm ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey, family=binomial("logit"))

# singularity warning, so use maximal complex random intercepts instead
model_glmer_physicalwarm2 <- glmer(rank_glmer_physicalwarm ~ robot_type + (1 | ParticipantID) + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit"))

# still warning, reduce
model_glmer_physicalwarm3 <- glmer(rank_glmer_physicalwarm ~ robot_type + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit"))

# allfit command
model_allfit_physwarm1 <- allFit(model_glmer_physicalwarm1)
# -> neldermead doesnt issue warning

# use nelder mead
model_glmer_physicalwarm_nm <- glmer(rank_glmer_physicalwarm ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey, family=binomial("logit"), control = glmerControl(optimizer="Nelder_Mead")) # no singularity warning 

summary(model_glmer_physicalwarm_nm) # not significant

# wald CI
confint(model_glmer_physicalwarm_nm,parm="beta_",method="Wald")
```

## Safety
```{r}
model_glmer_safety1 <- glmer(rank_glmer_safety ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey, family=binomial("logit"))

# singularity warning, so use maximal complex random intercepts instead
model_glmer_safety2 <- glmer(rank_glmer_safety ~ robot_type + (1 | ParticipantID) + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit"))

# still warning, reduce
model_glmer_safety3 <- glmer(rank_glmer_safety ~ robot_type + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit"))

# allfit command
model_allfit_safety1 <- allFit(model_glmer_safety1)
# -> nmkbw doesnt issue warning

# use nmkbw
model_glmer_safety_nmkbw <- glmer(rank_glmer_safety ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey, family=binomial("logit"), control = glmerControl(optimizer="nmkbw")) # no singularity warning 

summary(model_glmer_safety_nmkbw) # not significant

# wald CI
confint(model_glmer_safety_nmkbw,parm="beta_",method="Wald")
```

## Social competence
```{r}
model_glmer_socialcomp1 <- glmer(rank_glmer_socialcompetence ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey, family=binomial("logit"))

summary(model_glmer_socialcomp1) # not significant

# wald CI
confint(model_glmer_socialcomp1,parm="beta_",method="Wald")
```

## Social intelligence
```{r}
model_glmer_socialint1 <- glmer(rank_glmer_socialintelligence ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey, family=binomial("logit"))

# singularity warning, so use maximal complex random intercepts instead
model_glmer_socialint2 <- glmer(rank_glmer_socialintelligence ~ robot_type + (1 | ParticipantID) + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit"))

# still warning, reduce
model_glmer_socialint3 <- glmer(rank_glmer_socialintelligence ~ robot_type + (1 | ParticipantID:robot_type) + (1| robot), data = df_survey, family=binomial("logit"))

# allfit command
model_allfit_socialint1 <- allFit(model_glmer_socialint1)
### save summary in new object
summ_allfit_socialint1 <- summary(model_allfit_socialint1) 
### look at fixed estimates
summ_allfit_socialint1$fixef # differences relatively small
### look at random effect
summ_allfit_socialint1$sdcor # differences small
### check log likelihood
summ_allfit_socialint1$llik # differences small
### check whether all model ran
summ_allfit_socialint1$which.OK # all ran 
# continue with singularity warning

summary(model_glmer_socialint1) # not significant

# wald CI
confint(model_glmer_socialint1,parm="beta_",method="Wald")
```

## Socialness
```{r}
model_glmer_social1 <- glmer(rank_glmer_social ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey, family=binomial("logit"))

summary(model_glmer_social1) # not significant

# wald CI
confint(model_glmer_social1,parm="beta_",method="Wald")
```

## Social warmth
```{r}
model_glmer_socialwarm1 <- glmer(rank_glmer_socialwarmth ~ robot_type + (1 + robot_type| ParticipantID) + (1| robot), data = df_survey, family=binomial("logit"))

summary(model_glmer_socialwarm1) # not significant

# wald CI
confint(model_glmer_socialwarm1,parm="beta_",method="Wald")
```